---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# infosiga

<!-- badges: start -->
[![Lifecycle: stable](https://img.shields.io/badge/lifecycle-stable-brightgreen.svg)](https://lifecycle.r-lib.org/articles/stages.html#stable)
<!-- badges: end -->

The goal of `infosiga` is to provide three datasets related to road crashes that happened in the State of São Paulo, Brazil, from the Infosiga.SP data repository. These data includes attributes from the crashes (`infosiga_sinistros`), victims (`infosiga_vitimas`) and vehicles (`infosiga_veiculos`).

## Installation

You can install the development version of infosiga from [GitHub](https://github.com/) with:

``` r
# install.packages("pak")
pak::pak("pabsantos/infosiga")
```

## Example

This is a basic example which shows how to use this package:

```{r example}
library(infosiga)
str(infosiga_sinistros)
```

# Citation

```{r citation}
citation("infosiga")
```
